---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# entrymodels

<!-- badges: start -->
![CRAN version](https://www.r-pkg.org/badges/version/entrymodels)
[![Travis build status](https://travis-ci.org/gnjardim/entrymodels.svg?branch=master)](https://travis-ci.org/gnjardim/entrymodels)
<!-- badges: end -->

Tools for measuring empirically the effects of entry in concentrated markets, based in Bresnahan and Reiss (1991). 

## Installation

You can install the released version of entrymodels from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("entrymodels")
```

And the development version from [GitHub](https://github.com/gnjardim/entrymodels) with:

``` r
# install.packages("devtools")
devtools::install_github("gnjardim/entrymodels")
```
Which should return something similar to:

``` r
* installing *source* package 'entrymodels' ...
** using staged installation
** R
** inst
** byte-compile and prepare package for lazy loading
** help
*** installing help indices
  converting help for package 'entrymodels'
    finding HTML links ... done
    aux_matrix                              html  
    br1                                     html  
    em_basic                                html  
    load_example_data                       html  
** building package indices
** testing if installed package can be loaded from temporary location
*** arch - i386
*** arch - x64
** testing if installed package can be loaded from final location
*** arch - i386
*** arch - x64
** testing if installed package keeps a record of temporary installation path
* DONE (entrymodels)
```

Please note that you should have [Rtools](http://cran.r-project.org/bin/windows/Rtools/) installed. 

## Example

This is a basic example which shows you how to estimate a basic entry model with our sample data.

```{r example, message = FALSE}
library(entrymodels)

tb <- load_example_data()
(em <- em_basic(tb, "Populacao", "n_agencias"))
```

