---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# entrymodels

<!-- badges: start -->
![CRAN version](https://www.r-pkg.org/badges/version/entrymodels)
![License](https://img.shields.io/github/license/gnjardim/entrymodels)
<!-- badges: end -->

Tools for measuring empirically the effects of entry in concentrated markets, based in Bresnahan and Reiss (1991). 

## Installation

You can install the released version of entrymodels from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("entrymodels")
```

And the development version from [GitHub](https://github.com/gnjardim/entrymodels) with:

``` r
# install.packages("devtools")
devtools::install_github("gnjardim/entrymodels")
```
## Example

This is a basic example which shows you how to estimate a basic entry model with our sample data.

```{r example, message = FALSE}
library(entrymodels)

tb <- load_example_data()
(em <- em_basic(tb, "Populacao", "n_agencias"))
```

